---
title: "This file Analysizes the Value Function of the Planner from Simulated Results"
output: 
  html_notebook:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)

library(tidyverse)
library(REconTools)
```

# Analyze Planner Value

## Import Data

```{r}
mt_plan_v_tilde <- read.csv('C:/Users/fan/Documents/Dropbox (UH-ECON)/PrjNygaardSorensenWang/Output/snwx_v_planner_small.csv', header=FALSE)
ar_st_varnames <- c('age', 'marital', 'kids', 'checks',	'ymin', 'ymax', 'mass', 'survive', 'vtilde', 'ctilde')
tb_plan_v_tilde <- as_tibble(mt_plan_v_tilde) %>%
  rename_all(~c(ar_st_varnames)) %>%
  rowid_to_column(var = "id") %>%
  filter(vtilde != 0)

# Column 1: Age (in year before COVID)
# Column 2: Marital status (0 if not married; 1 if married)
# Column 3: Nr of kids (0, 1, ..., 5) where 5 means 5 or more
# Column 4: Number of welfare checks (here either equal to 0 or 1)
# Column 5 and column 6 give income range
# So the individual's income is at least as large as the value in column 5 but strictly less than the value in column 6
# Column 7: Population weight Of that particular group (in the stationary distribution)
# Column 8: Survival probability of that particular age (since the planner knows that some of the individuals will die before next period, so wasn't sure how you wanted me to include that. I did not already include it in V^tilde)
# Column 9: Value of planner as in the slides (with the exception that I didn't multiply by the survival probability
```

## Generate A and alpha file version

```{r}
tb_plan_v_tilde_a_alpha <- tb_plan_v_tilde %>% 
  arrange(age, marital, kids, ymin, checks, vtilde, ctilde) %>%
  group_by(age, marital, kids, ymin) %>%
  mutate(vtilde_lead = lead(vtilde), 
         ctilde_lead = lead(ctilde)) %>%
  filter(checks != max(tb_plan_v_tilde$checks)) %>%
  rename(V_A_i = vtilde, C_A_i = ctilde) %>%
  mutate(V_alpha_i = vtilde_lead - V_A_i, 
         C_alpha_i = ctilde_lead - C_A_i) %>%
  mutate(checks = checks + 1) %>%
  ungroup()
print(tb_plan_v_tilde_a_alpha)
```

#### Summarize All Columns Unconditional

```{r}
REconTools::ff_summ_percentiles(tb_plan_v_tilde_a_alpha, bl_statsasrows = FALSE)
```

#### Summarize All Columns by Checks

Will summarize all varaibles by 4 different check amounts, the four check increments are (each is worth 200 dollars):

```{r}
# Unique Checks:
ar_checks <- sort(unique(tb_plan_v_tilde_a_alpha %>% pull(checks)))
ar_checks_4 <- ar_checks[seq(1, length(ar_checks), length.out=4)]
mt_checks_4 <- ar_checks_4
dim(mt_checks_4) <- c(length(ar_checks_4), 1)
mt_checks*200
```

Now summarize by these check amounts:

```{r}
# Summarize all Variables Each Check:
ls_stats_by_checks = suppressWarnings(
  apply(mt_checks_4, 1,
        function(row) {
          fl_check = row[1]
          REconTools::ff_summ_percentiles(
            tb_plan_v_tilde_a_alpha %>% 
              filter(checks == fl_check), 
            bl_statsasrows = FALSE)
        }))

# Print Stats
print(ls_stats_by_checks)
```

#### Joint distribution of A and alpha by Check (Show Only for Four Checks)

##### Joint Distribution of Effects on Consumption 

```{r}
# Generate Gap Variable
dft_graph <- tb_plan_v_tilde_a_alpha %>%
  filter(checks %in% ar_checks_4) %>%
  mutate(marital = as.factor(marital),
         kids = as.factor(kids))

# Titling
st_title <- sprintf("2020 Consumption without Binary Check and Marginal Effects of Checks")
title_line1 <- sprintf("Each circle (cross) represents an Age/Marriage/Child/Income/Check Type")
title <- expression('The joint distribution of'~A[i]~'and'~alpha[i]~', Checks, SNW 2020')
caption <- paste0('Life Cycle Simulation.')
# Labels
st_x_label <- expression('Cons 2020 without the Next Increment of Checks')
st_y_label <- expression('Marginal C from An Additional Check')

# Binary Marginal Effects and Prediction without Binary
plt_A_alpha <- dft_graph %>% ggplot(aes(x=C_A_i)) +
      geom_point(aes(y=C_alpha_i,
                     color=factor(checks))) +
      geom_abline(intercept = 0, slope = 1) + # 45 degree line
      labs(title = st_title,
           subtitle = paste0(title_line1),
           x = st_x_label,
           y = st_y_label,
           caption = caption) 
# Labeling
plt_A_alpha$labels$color <- "checks"

print(plt_A_alpha)
```

##### Joint Distribution of Effects on Value 

```{r}
# Generate Gap Variable
dft_graph <- tb_plan_v_tilde_a_alpha %>%
  filter(checks %in% ar_checks_4) %>%
  mutate(marital = as.factor(marital),
         kids = as.factor(kids))

# Titling
st_title <- sprintf("Value (Life-Time) without Binary Check and Marginal Effects of Checks")
title_line1 <- sprintf("Each circle (cross) represents an Age/Marriage/Child/Income/Check Type")
title <- expression('The joint distribution of'~A[i]~'and'~alpha[i]~', Checks, SNW 2020')
caption <- paste0('Life Cycle Simulation.')
# Labels
st_x_label <- expression('Life-time Utility without the Next Increment of Checks')
st_y_label <- expression('Marginal V from An Additional Check')

# Binary Marginal Effects and Prediction without Binary
plt_A_alpha <- dft_graph %>% ggplot(aes(x=V_A_i)) +
      geom_point(aes(y=V_alpha_i,
                     color=factor(checks))) +
      geom_abline(intercept = 0, slope = 1) + # 45 degree line
      labs(title = st_title,
           subtitle = paste0(title_line1),
           x = st_x_label,
           y = st_y_label,
           caption = caption) 
# Labeling
plt_A_alpha$labels$color <- "checks"

print(plt_A_alpha)
```

#### Joint distribution of A and alpha by Income Groups

```{r}
# Select 4 Y groups Levels
ar_ymin <- sort(unique(tb_plan_v_tilde_a_alpha %>% pull(ymin)))
ar_ymin <- ar_ymin[seq(1, length(ar_ymin), length.out=4)]

dft_graph_subset <- dft_graph %>% filter(checks %in% ar_checks_4) %>% filter(ymin %in% ar_ymin) 

# Binary Marginal Effects and Prediction without Binary
st_title <- sprintf("BY FOUR Y GROUPS: Expected C without Binary Check and Marginal C Effects of Checks")
plt_A_alpha_grp <- dft_graph_subset %>% ggplot(aes(x=V_A_i)) +
      geom_point(aes(y=V_alpha_i,
                     color=factor(checks))) +
      geom_abline(intercept = 0, slope = 1) + # 45 degree line
      facet_wrap(~ ymin, nrow=2) +
      labs(title = st_title,
           subtitle = paste0(title_line1),
           x = st_x_label,
           y = st_y_label,
           caption = caption) 

# Labeling
plt_A_alpha_grp$labels$color <- "checks"

print(plt_A_alpha_grp)
```

#### f(A,alpha), color=age, panel=ymin

```{r}
# Select 4 Y groups Levels
ar_age <- sort(unique(dft_graph %>% pull(age)))
ar_age <- ar_age[seq(1, 30, length.out=4)]
ar_ymin <- sort(unique(dft_graph %>% pull(ymin)))
ar_ymin <- ar_ymin[c(15, 20, 25, 30)]

dft_graph_subset <- dft_graph %>% 
  filter(ymin %in% ar_ymin) %>%
  filter(checks == 1) %>%
  filter(marital == 0) %>%
  filter(kids == 1)

# Binary Marginal Effects and Prediction without Binary
st_title <- sprintf("Color=Age, Panel=Y ; Married + 1 Kid + First Check")
plt_A_alpha_grp <- dft_graph_subset %>% ggplot(aes(x=A_i)) +
      geom_point(aes(y=alpha_i,
                     color=factor(age)), size=4) +
      geom_abline(intercept = 0, slope = 1) + # 45 degree line
      facet_wrap(~ ymin, nrow=2) +
      labs(title = st_title,
           subtitle = paste0(title_line1),
           x = st_x_label,
           y = st_y_label,
           caption = caption) 

# Labeling
plt_A_alpha_grp$labels$color <- "age"

print(plt_A_alpha_grp)
```

#### f(A,alpha), color=checks, panel=ymin

```{r}
# Select 4 Y groups Levels
ar_checks <- sort(unique(tb_plan_v_tilde_a_alpha %>% pull(checks)))
ar_checks <- ar_checks[seq(1, length(ar_checks), length.out=4)]
ar_age <- sort(unique(dft_graph %>% pull(age)))
ar_age <- ar_age[seq(1, 30, length.out=4)]
ar_ymin <- sort(unique(dft_graph %>% pull(ymin)))
ar_ymin <- ar_ymin[c(30)]

dft_graph_subset <- dft_graph %>% 
  filter(ymin %in% ar_ymin) %>%
  filter(marital == 0) %>%
  filter(age == 50) %>%
  filter(kids %in% c(1))

# Binary Marginal Effects and Prediction without Binary
st_title <- sprintf("Color=Age, Panel=Y ; Married + 1 Kid + First Check")
plt_A_alpha_grp <- dft_graph_subset %>% ggplot(aes(x=A_i)) +
      geom_point(aes(y=alpha_i,
                     color=factor(checks)), size=4) +
      geom_abline(intercept = 0, slope = 1) + # 45 degree line
      facet_wrap(~ kids, nrow=2) +
      labs(title = st_title,
           subtitle = paste0(title_line1),
           x = st_x_label,
           y = st_y_label,
           caption = caption) 

# Labeling
plt_A_alpha_grp$labels$color <- "age"

print(plt_A_alpha_grp)
```
## Value Summarize and Tabulate (Both Check no Check)

Aggregate Statistics:

```{r}
REconTools::ff_summ_percentiles(tb_plan_v_tilde, bl_statsasrows = FALSE)
```

### Group Stats by Income 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('ymin','age')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Age 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('age')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Kids

```{r}
df <- tb_plan_v_tilde
vars.group <- c('kids')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Marital Status


```{r}
df <- tb_plan_v_tilde
vars.group <- c('marital')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```
### Group Stats by Age and Marital Status

```{r}
df <- tb_plan_v_tilde
vars.group <- c('age', 'marital')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Age and Marital Status and Kids

```{r}
df <- tb_plan_v_tilde
vars.group <- c('age', 'marital', 'kids')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

## Summarize and Tabulate (Compare Check no Check)

### Group Stats by Income and Checks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('ymin')
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

A1 and A0 stats: 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('ymin', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```
### Group Stats by Age and Checks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('age')
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

A1 and A0 stats: 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('age', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Kids Checks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('kids')
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

V with check and V without Check Statistics:

```{r}
df <- tb_plan_v_tilde
vars.group <- c('kids', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Marital Status and CHecks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('marital')
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

A1 and A0 stats: 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('marital', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Age and Marital Status and CHecks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('age', 'marital' )
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

A1 and A0 stats: 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('age', 'marital', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

### Group Stats by Marital Status and kids and CHecks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('marital', 'kids' )
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

A1 and A0 stats: 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('marital', 'kids', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```


### Group Stats by Age and Marital Status and Kids and Checks

alpha statistics: 

```{r}
df <- tb_plan_v_tilde_a_alpha
vars.group <- c('age', 'marital', 'kids')
var.numeric <- 'alpha_i'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

A1 and A0 stats: 

```{r}
df <- tb_plan_v_tilde
vars.group <- c('age', 'marital', 'kids', 'checks')
var.numeric <- 'vtilde'
str.stats.group <- 'allperc'
ar.perc <- c(0.05, 0.25, 0.5, 0.75, 0.95)
ls_summ_by_group <- REconTools::ff_summ_bygroup(df, vars.group, var.numeric, str.stats.group, ar.perc)
ls_summ_by_group$df_table_grp_stats
```

## Graphs

### Graph Probability Mass 

```{r}
# select variables
tb_graph <- tb_plan_v_tilde %>% 
  select(mass, age, marital, kids, checks) %>%
  mutate(marital = as.factor(marital),
         kids = as.factor(kids),
         checks = as.factor(checks))

# graph
lineplot <- tb_graph %>%
  group_by(checks, age, marital, kids) %>%
  summarise(mean_mass = sum(mass)) %>%
  gather(variable, value, -checks, -age, -marital, -kids) %>%
  ggplot(aes(x=age, y=value,
             colour=checks, linetype=checks, shape=checks)) +
  facet_wrap( ~ marital + kids, nrow=2) +
  geom_line() +
  geom_point() +
  labs(title = paste0('Mass at States'),
       x = 'Age',
       y = 'Mass',
       caption = 'SVW 2020')
# graph
print(lineplot)

```

### Graph Value Statistics By Various Statistics

```{r}
# select variables
tb_graph <- tb_plan_v_tilde %>% 
  select(vtilde, age, mass, marital, kids, checks) %>%
  mutate(marital = as.factor(marital),
         kids = as.factor(kids),
         checks = as.factor(checks))

# graph
lineplot <- tb_graph %>%
  group_by(checks, age, marital, kids) %>%
  summarise(mean_vtilde = mean(vtilde*(mass/sum(mass)))) %>%
  gather(variable, value, -checks, -age, -marital, -kids) %>%
  ggplot(aes(x=age, y=value,
             colour=checks, linetype=checks, shape=checks)) +
  facet_wrap( ~ marital + kids, nrow=2) +
  geom_line() +
  geom_point() +
  labs(title = paste0('Planner Value by Checks'),
       x = 'Age',
       y = 'Planner Exp Value',
       caption = 'SVW 2020')
# graph
print(lineplot)

```

