---
title: |
  | Optimal Feasible Allocation
  | Conditional on Income, Marital Status and Kids Count
  | moredense_a100zh266_e2m2 vs moredense_a65zh266zs5_e2m2_b1_calibrated
  | ybin = 2500
output:
  html_notebook:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
---

```{r setup, include=FALSE}
# rm(list = ls())

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)

library(tidyverse)
library(REconTools)
```

# Optimal Feasible Allocation

2019 Income, Kids Count and Martial Status (non-stochastic) based optimal linear allocation (Utilitarian). Will solve for feasible optimal allocation results given different simulation structures:

1. Simulate without spousal productivity shocks
2. Simulate with spousal productivity shocks

Common Graph Title First Line Prefix

```{r}
slb_add_title_round1 = 'Round One Policy, '
slb_add_title_round2 = 'Round Two Policy, '
slb_subtitle_stack_2nd = 'optimal2nd_total = 1st actual + 2nd round optimal (given 1st actual) '
slb_subtitle_joint_1st2nd = 'optimal 1st and 2nd rounds (given 1st actual) '
```

Files:

```{r}
# # File Names
# st_file_type_withspouse_shock <- 'moredense_ybin25000'
# snm_simu_csv_withspouse_shock <- paste0('snwx_v_planner_',st_file_type_withspouse_shock,'.csv')

# # File Names
# st_file_type_withspouse_shock <- 'dense_ybin2500'
# snm_simu_csv_withspouse_shock <- paste0('snwx_v_planner_',st_file_type_withspouse_shock,'.csv')

# File Names
# st_file_type_withspouse_shock <- 'moredense_a100zh81zs5_e2m2'
# st_file_type_withspouse_shock <- 'moredense_a65zh133zs5_e2m2'
# st_file_type_withspouse_shock <- 'moredense_a65zh266zs5_e2m2'
# st_file_type_withspouse_shock <- 'moredense_a65zh266zs5_e2m2_b0_calibrated'
# st_file_type_withspouse_shock <- 'moredense_a65zh266zs5_e2m2_b1_calibrated'
# snm_simu_csv_withspouse_shock <- paste0('snwx_v_planner_',st_file_type_withspouse_shock,'.csv')

ls_output <- fs_opti_support()
st_file_type_withspouse_shock <- ls_output$st_file_type_withspouse_shock
snm_simu_csv_withspouse_shock <- ls_output$snm_simu_csv_withspouse_shock
srt_simu_path <- ls_output$srt_simu_path
bl_save_img <- ls_output$bl_save_img
spt_img_save <- ls_output$spt_img_save
srt_csv_path <- ls_output$srt_csv_path
```


## Common Parameters Across

```{r}
# Max Phase Out given 1200*2 + 500*4 = 4400
fl_max_phaseout = 238000
it_bin_dollar_before_phaseout = 2500
# Dollar Per Check
fl_percheck_dollar = 100
# Meaning of Ymin Ymax simulated interval of 1
fl_multiple = 58056
# Number of Max Checks
it_max_checks_1st = 44
it_max_checks_2nd = 88
# Number of Tax Paying Households
fl_tax_hh = 128580000
# Number of Income Groups to Use: use 25 for 10,000 = 1
# Age Conditions
# it_max_age = 64
# it_min_age = 64
it_max_age = 64
it_min_age = 18
it_age_bins = 1
# Image Save Suffix
st_img_suf_age_ybin <- paste0(it_min_age, 't', it_max_age)
```

### Variable Names and Paths

```{r}
# File Path
# srt_simu_path <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/PrjNygaardSorensenWang/Output/'

# Column Names
ar_svr_csv <- c('age', 'marital', 'kids', 'checks',	'ymin', 'mass', 'survive', 'vtilde', 'ctilde')
# Variables That Identify Individual Types
ar_svr_groups <- c('marital', 'kids', 'age_group', 'ymin_group')
ar_svr_groups_noage <- c('marital', 'kids', 'ymin_group')
ar_svr_groups_stats <- c('mass', 'survive')
# Number of Checks and Planner Value
svr_checks <- 'checks'
svr_v_value <- 'vtilde'
svr_c_value <- 'ctilde'
svr_mass <- 'mass'
```

Image and Save Control

```{r}
# Images to Save
ls_st_save_imgs = c('mass', 'mc', 'checks_c', 'mv', 'checks_v')
# Save Folder
# bl_save_img <- TRUE
# spt_img_save <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/PrjNygaardSorensenWang/Results/2020-08-05/Graphs/'
# srt_csv_path <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/PrjNygaardSorensenWang/Results/2020-08-05/csv/'
# # CSV and Image Paths
# spt_img_save = paste0(spt_img_save, st_file_type_withspouse_shock,'/')
# srt_csv_path = paste0(srt_csv_path, st_file_type_withspouse_shock,'/')
# dir.create(file.path(spt_img_save), showWarnings = FALSE, recursive = TRUE)
# dir.create(file.path(srt_csv_path), showWarnings = FALSE, recursive = TRUE)
# Save Size
it_img_width=300
it_img_height=180
st_img_units='mm'
it_img_res=300
it_img_pointsize=3
```

### Planner Preference

```{r}
ar_rho <- 1 - (10^(c(seq(-2,2, length.out=8))))
ar_rho <- unique(c(1,ar_rho))
# ar_rho <- c(1)
```

## Round 1 Results with Spousal Income Shocks

### Process

Call the input processing function

```{r}
# Call function
ls_prc_outputs_zs5_1st <- PrjOptiAlloc::ffp_snw_process_inputs(
  srt_simu_path = srt_simu_path,
  snm_simu_csv = snm_simu_csv_withspouse_shock,
  fl_max_phaseout = fl_max_phaseout,
  it_bin_dollar_before_phaseout = it_bin_dollar_before_phaseout,
  fl_percheck_dollar = fl_percheck_dollar,
  fl_multiple = fl_multiple,
  it_max_checks = it_max_checks_1st,
  fl_tax_hh = fl_tax_hh,
  it_max_age = it_max_age,
  it_min_age = it_min_age,
  it_age_bins = it_age_bins,
  ar_svr_csv = ar_svr_csv,
  ar_svr_groups = ar_svr_groups,
  ar_svr_groups_stats = ar_svr_groups_stats,
  svr_checks = svr_checks,
  svr_v_value = svr_v_value,
  svr_c_value = svr_c_value,
  svr_mass = svr_mass,
  ar_rho = ar_rho,
  bl_non_inc_adjust = TRUE,
  bl_print = FALSE,
  bl_print_verbose = FALSE)
```

### Outputs

REV:

```{r}
tb_rho_rev_c=ls_prc_outputs_zs5_1st$tb_rho_rev_c
tb_rho_rev_v=ls_prc_outputs_zs5_1st$tb_rho_rev_v
print(tb_rho_rev_c)
print(tb_rho_rev_v)
```

Allocation Results:

```{r}
df_input_il_noninc_covar_zs5_1st=ls_prc_outputs_zs5_1st$df_input_il_noninc_covar
df_alloc_i_long_covar_c_zs5_1st=ls_prc_outputs_zs5_1st$df_alloc_i_long_covar_c
df_alloc_i_long_covar_v_zs5_1st=ls_prc_outputs_zs5_1st$df_alloc_i_long_covar_v
```

Graph related:

```{r}
stg_subtitle=ls_prc_outputs_zs5_1st$stg_subtitle
stg_caption=ls_prc_outputs_zs5_1st$stg_caption
```

### Graphs

```{r}
allocate_type_levels <- c(Actual = "actual", Optimal = "optimal")
# Generic non feasible specific Figures
st_img_suffix <- paste0(st_file_type_withspouse_shock, '_', st_img_suf_age_ybin, '_round1_feasible')
ls_pl_generic <- PrjOptiAlloc::ffp_snw_graph_feasible(ar_rho=ar_rho,
                                df_input_il_noninc_covar=df_input_il_noninc_covar_zs5_1st,
                                df_alloc_i_long_covar_c=
                                  df_alloc_i_long_covar_c_zs5_1st %>%
                                  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels)),
                                df_alloc_i_long_covar_v=
                                  df_alloc_i_long_covar_v_zs5_1st %>%
                                  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels)),
                                ls_st_save_imgs = c('mass', 'mc', 'mv', 'mlogc'),
                                st_file_type = st_file_type_withspouse_shock,
                                slb_add_title = slb_add_title_round1,
                                stg_subtitle=stg_subtitle, stg_caption=stg_caption,
                                it_img_width=it_img_width, it_img_height=it_img_height,
                                st_img_units='mm', it_img_res=it_img_res, it_img_pointsize=it_img_pointsize,
															  st_img_suffix=st_img_suffix, bl_save_img=bl_save_img,
															  spt_img_save=spt_img_save)
# Generate Graphs
st_img_suffix <- paste0(st_file_type_withspouse_shock, '_', st_img_suf_age_ybin, '_round1_feasible')
ls_pl <- PrjOptiAlloc::ffp_snw_graph_feasible(ar_rho=ar_rho,
                                df_input_il_noninc_covar=df_input_il_noninc_covar_zs5_1st,
                                df_alloc_i_long_covar_c=
                                  df_alloc_i_long_covar_c_zs5_1st %>%
                                  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels)),
                                df_alloc_i_long_covar_v=
                                  df_alloc_i_long_covar_v_zs5_1st %>%
                                  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels)),
                                ls_st_save_imgs = c('checks_cjv', 'checks_c', 'checks_v'),
                                st_file_type = st_file_type_withspouse_shock,
                                slb_add_title = slb_add_title_round1,
                                stg_subtitle=stg_subtitle, stg_caption=stg_caption,
                                it_img_width=it_img_width, it_img_height=it_img_height,
                                st_img_units='mm', it_img_res=it_img_res, it_img_pointsize=it_img_pointsize,
															  st_img_suffix=st_img_suffix, bl_save_img=bl_save_img,
															  spt_img_save=spt_img_save)
```

```{r}
# stg_title <- paste0(slb_add_title, '2020 Value and 2020 Consumption, Conditional on: Marry+Kids+Income, ', st_file_type)
# Combine frames
# df_alloc_i_long_covar_cjv <- rbind(
#     df_alloc_i_long_covar_v_zs5_1st %>%
#     filter(rho_val == ar_rho[1] & allocate_type == 'optimal') %>%
#     mutate(allocate_type = "1. optimal V"),
#     df_alloc_i_long_covar_c_zs5_1st %>%
#     filter(rho_val == ar_rho[1] & allocate_type == 'optimal') %>%
#     mutate(allocate_type = "2. optimal C")
#   )
# # graph mean check amount by income, marital status and kids counts
# plt_cur <- df_alloc_i_long_covar_cjv %>% ungroup() %>%
#   mutate(ymin_group = as.numeric(ymin_group),
#          kids = as.factor(kids),
#          marital = as.factor(marital)) %>%
#   ggplot(aes(x=ymin_group, y=checks*100,
#              colour=allocate_type,
#              shape=allocate_type,
#              linetype=allcate_type)) +
#   facet_wrap( ~ marital + kids, ncol=5, labeller = label_wrap_gen(multi_line=FALSE)) +
#   geom_point(size=3) +
#   geom_line()
# print(plt_cur)
```
#### Mass

```{r}
# Print Graphs
print(ls_pl$mass)
```

#### MC

##### Diff of Log

```{r}
print(ls_pl$mlogc)
```

##### Log of Diff

```{r}
print(ls_pl$mc)
```

#### Opti C

```{r}
print(ls_pl$checks_c)
```

#### MV

```{r}
print(ls_pl$mv)
```

#### Opti V

```{r}
print(ls_pl$checks_v)
```

## Round 2 Results with Spousal Income Shocks

```{r}
bl_given_firstcheck <- TRUE
```

### Process

Call the input processing function

```{r}
# Call function
ls_prc_outputs_zs5_2nd <- PrjOptiAlloc::ffp_snw_process_inputs(
  srt_simu_path = srt_simu_path,
  snm_simu_csv = snm_simu_csv_withspouse_shock,
  fl_max_phaseout = fl_max_phaseout,
  it_bin_dollar_before_phaseout = it_bin_dollar_before_phaseout,
  fl_percheck_dollar = fl_percheck_dollar,
  fl_multiple = fl_multiple,
  it_max_checks = it_max_checks_2nd,
  fl_tax_hh = fl_tax_hh,
  it_max_age = it_max_age,
  it_min_age = it_min_age,
  it_age_bins = it_age_bins,
  ar_svr_csv = ar_svr_csv,
  ar_svr_groups = ar_svr_groups,
  ar_svr_groups_stats = ar_svr_groups_stats,
  svr_checks = svr_checks,
  svr_v_value = svr_v_value,
  svr_c_value = svr_c_value,
  svr_mass = svr_mass,
  ar_rho = ar_rho,
  bl_given_firstcheck = bl_given_firstcheck,
  bl_non_inc_adjust = TRUE,
  bl_print = FALSE,
  bl_print_verbose = FALSE)
```

### Outputs

REV:

```{r}
tb_rho_rev_c=ls_prc_outputs_zs5_2nd$tb_rho_rev_c
tb_rho_rev_v=ls_prc_outputs_zs5_2nd$tb_rho_rev_v
print(tb_rho_rev_c)
print(tb_rho_rev_v)
```

```{r}
df_input_il_noninc_covar_zs5_2nd=ls_prc_outputs_zs5_2nd$df_input_il_noninc_covar
df_alloc_i_long_covar_c_zs5_2nd=ls_prc_outputs_zs5_2nd$df_alloc_i_long_covar_c
df_alloc_i_long_covar_v_zs5_2nd=ls_prc_outputs_zs5_2nd$df_alloc_i_long_covar_v
stg_subtitle=ls_prc_outputs_zs5_2nd$stg_subtitle
stg_caption=ls_prc_outputs_zs5_2nd$stg_caption
```

### Graphs

#### Graph Round Two MV and MC

```{r}
# Generate Graphs
stg_subtitle_stack=paste0(slb_subtitle_stack_2nd, stg_subtitle)
st_img_suffix <- paste0(st_file_type_withspouse_shock, '_', st_img_suf_age_ybin, '_round2_feasible')
ls_pl_r2 <- PrjOptiAlloc::ffp_snw_graph_feasible(ar_rho=ar_rho,
                                df_input_il_noninc_covar=df_input_il_noninc_covar_zs5_2nd,
                                df_alloc_i_long_covar_c=df_alloc_i_long_covar_c_zs5_2nd,
                                df_alloc_i_long_covar_v=df_alloc_i_long_covar_v_zs5_2nd,
                                ls_st_save_imgs = c('mv', 'mc', 'mlogc'),
                                st_file_type = st_file_type_withspouse_shock,
                                slb_add_title = slb_add_title_round2,
                                stg_subtitle=stg_subtitle_stack, stg_caption=stg_caption,
                                it_img_width=it_img_width, it_img_height=it_img_height,
                                st_img_units='mm', it_img_res=it_img_res, it_img_pointsize=it_img_pointsize,
															  st_img_suffix=st_img_suffix, bl_save_img=bl_save_img,
															  spt_img_save=spt_img_save)
```

#### Graph Round One Actual + Round Two Optimal vs Round 1/2 Actual

Assume Round 1 actual duplicated in Round 2.

```{r}
# Labels
allocate_type_levels <- c("Opti 2nd + Actual 1st" = "opti2nd_total", "Actual 1st" = "actual")
slb_subtitle_stack1st2nd = ''
# Update Consumption Frame
df_alloc_i_long_covar_c_zs5_2nd_stack <- df_alloc_i_long_covar_c_zs5_2nd %>%
  group_by(rho, id_i) %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks) %>%
  mutate(total = optimal + actual) %>%
  rename(checks_optimal = optimal,
         checks_actual = actual,
         checks_opti2nd_total = total) %>%
  pivot_longer(cols = starts_with('checks'),
               names_to = c('allocate_type'),
               names_pattern = paste0("checks_(.*)"),
               values_to = "checks") %>%
  filter(allocate_type != 'optimal') %>%
  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels))

# Update Value Frame
df_alloc_i_long_covar_v_zs5_2nd_stack <- df_alloc_i_long_covar_v_zs5_2nd %>%
  group_by(rho, id_i) %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks) %>%
  mutate(total = optimal + actual) %>%
  rename(checks_optimal = optimal,
         checks_actual = actual,
         checks_opti2nd_total = total) %>%
  pivot_longer(cols = starts_with('checks'),
               names_to = c('allocate_type'),
               names_pattern = paste0("checks_(.*)"),
               values_to = "checks") %>%
  filter(allocate_type != 'optimal') %>%
  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels))

# Generate Graphs
stg_subtitle_stack=paste0(slb_subtitle_stack_2nd, stg_subtitle)
st_img_suffix <- paste0(st_file_type_withspouse_shock, '_', st_img_suf_age_ybin, '_round2_feasible_stack')
ls_pl_stack <- PrjOptiAlloc::ffp_snw_graph_feasible(ar_rho=ar_rho,
                                df_input_il_noninc_covar=df_input_il_noninc_covar_zs5_2nd,
                                df_alloc_i_long_covar_c=df_alloc_i_long_covar_c_zs5_2nd_stack,
                                df_alloc_i_long_covar_v=df_alloc_i_long_covar_v_zs5_2nd_stack,
                                ls_st_save_imgs = c('checks_c', 'checks_v'),
                                st_file_type = st_file_type_withspouse_shock,
                                slb_add_title = slb_add_title_round2,
                                stg_subtitle=stg_subtitle_stack, stg_caption=stg_caption,
                                it_img_width=it_img_width, it_img_height=it_img_height,
                                st_img_units='mm', it_img_res=it_img_res, it_img_pointsize=it_img_pointsize,
															  st_img_suffix=st_img_suffix, bl_save_img=bl_save_img,
															  spt_img_save=spt_img_save)
```

#### Graph Round One Actual + Round Two Optimal vs Round 1 times 2

Same Round One Actual + Round Two Optimal as above, but for the alternative allocation, rather than plotting only one red line for 2nd round actual (assuming second round follows the first round), plot second round actual as the sum of first and second round (assuming second round follows the first round) actual.

```{r}
allocate_type_levels <- c("Optimal" = "opti2nd_total", "Actual" = "actual")
# Update Consumption Frame
df_alloc_i_long_covar_c_zs5_2nd_duplicate <- df_alloc_i_long_covar_c_zs5_2nd %>%
  group_by(rho, id_i) %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks) %>%
  mutate(total = optimal + actual, actual = actual*2) %>%
  rename(checks_optimal = optimal,
         checks_actual = actual,
         checks_opti2nd_total = total) %>%
  pivot_longer(cols = starts_with('checks'),
               names_to = c('allocate_type'),
               names_pattern = paste0("checks_(.*)"),
               values_to = "checks") %>%
  filter(allocate_type != 'optimal') %>%
  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels))
# Update Value Frame
df_alloc_i_long_covar_v_zs5_2nd_duplicate <- df_alloc_i_long_covar_v_zs5_2nd %>%
  group_by(rho, id_i) %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks) %>%
  mutate(total = optimal + actual, actual = actual*2) %>%
  rename(checks_optimal = optimal,
         checks_actual = actual,
         checks_opti2nd_total = total) %>%
  pivot_longer(cols = starts_with('checks'),
               names_to = c('allocate_type'),
               names_pattern = paste0("checks_(.*)"),
               values_to = "checks") %>%
  filter(allocate_type != 'optimal') %>%
  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels))
# Generate Graphs
stg_subtitle_stack=paste0(stg_subtitle)
st_img_suffix <- paste0(st_file_type_withspouse_shock, '_', st_img_suf_age_ybin, '_round2_feasible_duplicate')
ls_pl_duplicate <- PrjOptiAlloc::ffp_snw_graph_feasible(ar_rho=ar_rho,
                                df_input_il_noninc_covar=df_input_il_noninc_covar_zs5_2nd,
                                df_alloc_i_long_covar_c=df_alloc_i_long_covar_c_zs5_2nd_duplicate,
                                df_alloc_i_long_covar_v=df_alloc_i_long_covar_v_zs5_2nd_duplicate,
                                ls_st_save_imgs = c('checks_c', 'checks_v'),
                                st_file_type = st_file_type_withspouse_shock,
                                slb_add_title = slb_add_title_round2,
                                stg_subtitle=stg_subtitle_stack, stg_caption=stg_caption,
                                it_img_width=it_img_width, it_img_height=it_img_height,
                                st_img_units='mm', it_img_res=it_img_res, it_img_pointsize=it_img_pointsize,
															  st_img_suffix=st_img_suffix, bl_save_img=bl_save_img,
															  spt_img_save=spt_img_save)
```

#### Graph Compare Round 1 and 2 Optimal

```{r}
allocate_type_levels <- c("1st round" = "1st_round", "2nd round" = "2nd_round")
# Update Consumption Frame
df_alloc_i_long_covar_c_zs5_2nd_joint <- df_alloc_i_long_covar_c_zs5_2nd %>%
  group_by(rho, id_i) %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks) %>%
  rename(optimal_2nd_round = optimal) %>%
  left_join(df_alloc_i_long_covar_c_zs5_1st %>%
              filter( allocate_type == 'optimal') %>%
              select(id_i, rho, checks) %>%
              rename(optimal_1st_round = checks),
            by=setNames(c('id_i', 'rho'), c('id_i', 'rho'))) %>%
  select(-actual) %>%
  pivot_longer(cols = starts_with('optimal'),
               names_to = c('allocate_type'),
               names_pattern = paste0("optimal_(.*)"),
               values_to = "checks") %>%
  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels))
# Update Value Frame
df_alloc_i_long_covar_v_zs5_2nd_joint <- df_alloc_i_long_covar_v_zs5_2nd %>%
  group_by(rho, id_i) %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks) %>%
  rename(optimal_2nd_round = optimal) %>%
  left_join(df_alloc_i_long_covar_v_zs5_1st %>%
              filter( allocate_type == 'optimal') %>%
              select(id_i, rho, checks) %>%
              rename(optimal_1st_round = checks),
            by=setNames(c('id_i', 'rho'), c('id_i', 'rho'))) %>%
  select(-actual) %>%
  pivot_longer(cols = starts_with('optimal'),
               names_to = c('allocate_type'),
               names_pattern = paste0("optimal_(.*)"),
               values_to = "checks") %>%
  mutate(allocate_type = fct_recode(allocate_type, !!!allocate_type_levels))
# Generate Graphs
stg_subtitle_joint=paste0(slb_subtitle_joint_1st2nd, stg_subtitle)
st_img_suffix <- paste0(st_file_type_withspouse_shock, '_', st_img_suf_age_ybin, '_round2_feasible_joint')
ls_pl_joint <- PrjOptiAlloc::ffp_snw_graph_feasible(ar_rho=ar_rho,
                                df_input_il_noninc_covar=df_input_il_noninc_covar_zs5_2nd,
                                df_alloc_i_long_covar_c=df_alloc_i_long_covar_c_zs5_2nd_joint,
                                df_alloc_i_long_covar_v=df_alloc_i_long_covar_v_zs5_2nd_joint,
                                ls_st_save_imgs = c('checks_c', 'checks_v'),
                                st_file_type = st_file_type_withspouse_shock,
                                slb_add_title = slb_add_title_round2,
                                stg_subtitle=stg_subtitle_joint, stg_caption=stg_caption,
                                it_img_width=it_img_width, it_img_height=it_img_height,
                                st_img_units='mm', it_img_res=it_img_res, it_img_pointsize=it_img_pointsize,
															  st_img_suffix=st_img_suffix, bl_save_img=bl_save_img,
															  spt_img_save=spt_img_save)
```


#### MC Round 2

##### Diff of Log

```{r}
print(ls_pl_r2$mlogc)
```

##### Log of Diff

Given the number of checks individuals received in the first round, what is the Marginal Consumption from successive checks?

```{r}
print(ls_pl_r2$mc)
```

#### Opti C, 1st Actual + 2nd Optimal

```{r}
print(ls_pl_stack$checks_c)
```

#### Opti C, 1st Optimal cvs 2nd Optimal

```{r}
print(ls_pl_joint$checks_c)
```

#### Opti C, Actual Double

```{r}
print(ls_pl_duplicate$checks_c)
```

#### MV Round 2

```{r}
print(ls_pl_r2$mv)
```

#### Opti V, 1st Actual + 2nd Optimal

```{r}
print(ls_pl_stack$checks_v)
```

#### Opti V, 1st Optimal cvs 2nd Optimal

```{r}
print(ls_pl_joint$checks_v)
```

#### Opti V, Actual Double

```{r}
print(ls_pl_duplicate$checks_v)
```

## Print Results to CSV

### Print Allocation Results

Print Allocation Results in Two Ways, Row based, with actual, first, and second round allocations as columns. And this table is outputed, at different levels of aggregations. where the allocation columns are outputed as different weighted means. Also compute fraction 0, fraction at within group max.

```{r}

df_alloc_all <- rbind(
  ls_prc_outputs_zs5_1st$df_alloc_i_long_covar_v %>%
  filter(rho_val == ar_rho[1]) %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_v_1st',
                                   TRUE ~ allocate_type)),
  ls_prc_outputs_zs5_1st$df_alloc_i_long_covar_c %>%
  filter(rho_val == ar_rho[1]) %>%
  filter(allocate_type == 'optimal') %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_c_1st',
                                   TRUE ~ allocate_type)),
  ls_prc_outputs_zs5_2nd$df_alloc_i_long_covar_v %>%
  filter(rho_val == ar_rho[1]) %>%
  filter(allocate_type == 'optimal') %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_v_2nd',
                                   TRUE ~ allocate_type)),
  ls_prc_outputs_zs5_2nd$df_alloc_i_long_covar_c %>%
  filter(rho_val == ar_rho[1]) %>%
  filter(allocate_type == 'optimal') %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_c_2nd',
                                   TRUE ~ allocate_type))) %>%
  arrange(id_i, allocate_type) %>%
  select(-rho, -F_star_i, -EH_star_i, -survive) %>%
  select(id_i, rho_val, everything())

df_alloc_all <- df_alloc_all %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks)

# export
write.csv(df_alloc_all,
  paste0(srt_csv_path, "df_alloc_all_feasible.csv"),
  row.names = TRUE)

```

Export Grouped Average Statistics:

```{r}
ls_svr_groups <- ar_svr_groups
for (svr_group in ls_svr_groups) {

  # group mean
  df_alloc_combine_group_mean <- df_alloc_all %>%
    ungroup() %>% group_by(!!sym(svr_group)) %>%
    summarize(actual_mean = sum(actual*mass)/sum(mass),
              optimal_c_1st_mean = sum(optimal_c_1st*mass)/sum(mass),
              optimal_v_1st_mean = sum(optimal_v_1st*mass)/sum(mass),
              optimal_c_2nd_mean = sum(optimal_c_2nd*mass)/sum(mass),
              optimal_v_2nd_mean = sum(optimal_v_2nd*mass)/sum(mass),
              mass_sum = sum(mass))

  # Export
  write.csv(df_alloc_combine_group_mean,
    paste0(srt_csv_path, "df_alloc_",svr_group, "_feasible.csv"),
    row.names = TRUE)

  # All but Group mean
  ls_svr_groups_oneless <- ls_svr_groups[ls_svr_groups != svr_group]
  df_alloc_combine_group_mean_oneless <- df_alloc_all %>%
    ungroup() %>% group_by(!!!syms(ls_svr_groups_oneless)) %>%
    summarize(actual_mean = sum(actual*mass)/sum(mass),
              optimal_c_1st_mean = sum(optimal_c_1st*mass)/sum(mass),
              optimal_v_1st_mean = sum(optimal_v_1st*mass)/sum(mass),
              optimal_c_2nd_mean = sum(optimal_c_2nd*mass)/sum(mass),
              optimal_v_2nd_mean = sum(optimal_v_2nd*mass)/sum(mass),
              mass_sum = sum(mass))

  # Export
  write.csv(df_alloc_combine_group_mean_oneless,
    paste0(srt_csv_path, "df_alloc_",svr_group,"_without_feasible.csv"),
    row.names = TRUE)

}
```

Average Statistics without Age

```{r}
ls_svr_groups <- ar_svr_groups_noage
for (svr_group in ls_svr_groups) {

  # All but Group mean
  ls_svr_groups_oneless <- ls_svr_groups[ls_svr_groups != svr_group]
  df_alloc_combine_group_mean_oneless <- df_alloc_all %>%
    ungroup() %>% group_by(!!!syms(ls_svr_groups_oneless)) %>%
    summarize(actual_mean = sum(actual*mass)/sum(mass),
              optimal_c_1st_mean = sum(optimal_c_1st*mass)/sum(mass),
              optimal_v_1st_mean = sum(optimal_v_1st*mass)/sum(mass),
              optimal_c_2nd_mean = sum(optimal_c_2nd*mass)/sum(mass),
              optimal_v_2nd_mean = sum(optimal_v_2nd*mass)/sum(mass),
              mass_sum = sum(mass))

  # Export
  write.csv(df_alloc_combine_group_mean_oneless,
    paste0(srt_csv_path, "df_alloc_",svr_group,"_without_noage_feasible.csv"),
    row.names = TRUE)

}

```

### Print and save MASS REV results:

```{r}
# Save REV to table, Stack them
tb_rho_rev_mass_v1_tab <- ls_prc_outputs_zs5_1st$tb_rho_rev_v %>%
  mutate(objective = 'vlife',
         constraint = 'feasible',
         allocround = 'first')
tb_rho_rev_mass_c1_tab <- ls_prc_outputs_zs5_1st$tb_rho_rev_c %>%
  mutate(objective = 'c2020',
         constraint = 'feasible',
         allocround = 'first')
tb_rho_rev_mass_v2_tab <- ls_prc_outputs_zs5_2nd$tb_rho_rev_v %>%
  mutate(objective = 'vlife',
         constraint = 'feasible',
         allocround = 'second')
tb_rho_rev_mass_c2_tab <- ls_prc_outputs_zs5_2nd$tb_rho_rev_c %>%
  mutate(objective = 'c2020',
         constraint = 'feasible',
         allocround = 'second')
# Stack frames
tb_rho_rev_mass_v_c_tab <- rbind(tb_rho_rev_mass_v1_tab, tb_rho_rev_mass_c1_tab,
                                 tb_rho_rev_mass_v2_tab, tb_rho_rev_mass_c2_tab)
# export
write.csv(tb_rho_rev_mass_v_c_tab,
  paste0(srt_csv_path, "rev_feasible.csv"),
  row.names = TRUE)
```

## Notes
