---
title: |
  | Optimal Allocation
  | Conditional on Age (47 Age Groups One by One), Income, Marital Status and Kids Count
  | moredense_a100zh266_e2m2 vs moredense_a65zh266zs5_e2m2_b0_calibrated
  | ybin = 2500

output:
  html_notebook:
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
# rm(list = ls())

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)

library(tidyverse)
library(REconTools)
```

# Optimal Allocation

2019 Age, Income, Kids Count and Martial Status (non-stochastic) based optimal linear allocation (Utilitarian). Will solve for optimal allocation results given different simulation structures:

Each age one by one, to get the fully optimal age specific allocation. Do not graph.

Files:

```{r}
# # File Names
# st_file_type_withspouse_shock <- 'moredense_ybin25000'
# snm_simu_csv_withspouse_shock <- paste0('snwx_v_planner_',st_file_type_withspouse_shock,'.csv')

# # File Names
# st_file_type_withspouse_shock <- 'dense_ybin2500'
# snm_simu_csv_withspouse_shock <- paste0('snwx_v_planner_',st_file_type_withspouse_shock,'.csv')

# File Names
# st_file_type_withspouse_shock <- 'moredense_a100zh81zs5_e2m2'
# st_file_type_withspouse_shock <- 'moredense_a65zh133zs5_e2m2'
# st_file_type_withspouse_shock <- 'moredense_a65zh266zs5_e2m2'
# st_file_type_withspouse_shock <- 'moredense_a65zh266zs5_e2m2_b0_calibrated'
st_file_type_withspouse_shock <- 'moredense_a65zh266zs5_e2m2_b1_calibrated'

snm_simu_csv_withspouse_shock <- paste0('snwx_v_planner_',st_file_type_withspouse_shock,'.csv')
```

## Common Parameters Across

```{r}
# Max Phase Out given 1200*2 + 500*4 = 4400
fl_max_phaseout = 238000
it_bin_dollar_before_phaseout = 2500
# Dollar Per Check
fl_percheck_dollar = 100
# Meaning of Ymin Ymax simulated interval of 1
fl_multiple = 58056
# Number of Max Checks
it_max_checks_1st = 44
it_max_checks_2nd = 88
# Number of Tax Paying Households
fl_tax_hh = 128580000
# Number of Income Groups to Use: use 25 for 10,000 = 1
# Age Conditions
# it_max_age = 64
# it_min_age = 64
it_max_age = 64
it_min_age = 18
it_age_bins = 47
# Image Save Suffix
st_img_suf_age_ybin <- paste0(it_min_age, 't', it_max_age)
```

### Variable Names and Paths

```{r}
# File Path
srt_simu_path <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/PrjNygaardSorensenWang/Output/'

# Column Names
ar_svr_csv <- c('age', 'marital', 'kids', 'checks',	'ymin', 'mass', 'survive', 'vtilde', 'ctilde')
# Variables That Identify Individual Types
ar_svr_groups <- c('marital', 'kids', 'age_group', 'ymin_group')
ar_svr_groups_noage <- c('marital', 'kids', 'ymin_group')
ar_svr_groups_stats <- c('mass', 'survive')
# Number of Checks and Planner Value
svr_checks <- 'checks'
svr_v_value <- 'vtilde'
svr_c_value <- 'ctilde'
svr_mass <- 'mass'
```

Image and Save Control

```{r}
# Save Folder
srt_csv_path <- 'C:/Users/fan/Documents/Dropbox (UH-ECON)/PrjNygaardSorensenWang/Results/2020-08-05/csv/'
# CSV and Image Paths
srt_csv_path = paste0(srt_csv_path, st_file_type_withspouse_shock,'/')
dir.create(file.path(srt_csv_path), showWarnings = FALSE, recursive = TRUE)
```

### Planner Preference

```{r}
ar_rho <- 1 - (10^(c(seq(-2,2, length.out=8))))
ar_rho <- unique(c(1,ar_rho))
# ar_rho <- c(1)
```

## Round 1 Results with Spousal Income Shocks
  
### Process

Call the input processing function

```{r}
# Call function
ls_prc_outputs_zs5_1st <- PrjOptiAlloc::ffp_snw_process_inputs(
  srt_simu_path = srt_simu_path,
  snm_simu_csv = snm_simu_csv_withspouse_shock,
  fl_max_phaseout = fl_max_phaseout,
  it_bin_dollar_before_phaseout = it_bin_dollar_before_phaseout,
  fl_percheck_dollar = fl_percheck_dollar,
  fl_multiple = fl_multiple,
  it_max_checks = it_max_checks_1st,
  fl_tax_hh = fl_tax_hh,
  it_max_age = it_max_age,
  it_min_age = it_min_age,
  it_age_bins = it_age_bins,
  ar_svr_csv = ar_svr_csv,
  ar_svr_groups = ar_svr_groups,
  ar_svr_groups_stats = ar_svr_groups_stats,
  svr_checks = svr_checks,
  svr_v_value = svr_v_value,
  svr_c_value = svr_c_value,
  svr_mass = svr_mass,
  ar_rho = ar_rho,
  bl_non_inc_adjust = TRUE,
  bl_print = FALSE,
  bl_print_verbose = FALSE)
```

## Round 2 Results with Spousal Income Shocks

```{r}
bl_given_firstcheck <- TRUE
```

### Process

Call the input processing function

```{r}
# Call function
ls_prc_outputs_zs5_2nd <- PrjOptiAlloc::ffp_snw_process_inputs(
  srt_simu_path = srt_simu_path,
  snm_simu_csv = snm_simu_csv_withspouse_shock,
  fl_max_phaseout = fl_max_phaseout,
  it_bin_dollar_before_phaseout = it_bin_dollar_before_phaseout,
  fl_percheck_dollar = fl_percheck_dollar,
  fl_multiple = fl_multiple,
  it_max_checks = it_max_checks_2nd,
  fl_tax_hh = fl_tax_hh,
  it_max_age = it_max_age,
  it_min_age = it_min_age,
  it_age_bins = it_age_bins,
  ar_svr_csv = ar_svr_csv,
  ar_svr_groups = ar_svr_groups,
  ar_svr_groups_stats = ar_svr_groups_stats,
  svr_checks = svr_checks,
  svr_v_value = svr_v_value,
  svr_c_value = svr_c_value,
  svr_mass = svr_mass,
  ar_rho = ar_rho,
  bl_given_firstcheck = bl_given_firstcheck,
  bl_non_inc_adjust = FALSE,
  bl_print = FALSE,
  bl_print_verbose = FALSE)
```


## Print Results to CSV 

Only print a limited set of results, otherwise there would be too many rows. 

### Print Allocation Results 

Print Allocation Results in Two Ways, Row based, with actual, first, and second round allocations as columns. And this table is outputed, at different levels of aggregations. where the allocation columns are outputed as different weighted means. Also compute fraction 0, fraction at within group max. 

```{r}

df_alloc_all <- rbind(
  ls_prc_outputs_zs5_1st$df_alloc_i_long_covar_v %>% 
  filter(rho_val == ar_rho[1]) %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_v_1st',
                                   TRUE ~ allocate_type)),
  ls_prc_outputs_zs5_1st$df_alloc_i_long_covar_c %>% 
  filter(rho_val == ar_rho[1]) %>%
  filter(allocate_type == 'optimal') %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_c_1st',
                                   TRUE ~ allocate_type)),
  ls_prc_outputs_zs5_2nd$df_alloc_i_long_covar_v %>% 
  filter(rho_val == ar_rho[1]) %>%
  filter(allocate_type == 'optimal') %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_v_2nd',
                                   TRUE ~ allocate_type)),
  ls_prc_outputs_zs5_2nd$df_alloc_i_long_covar_c %>% 
  filter(rho_val == ar_rho[1]) %>%
  filter(allocate_type == 'optimal') %>%
  mutate(allocate_type = case_when(allocate_type == 'optimal' ~ 'optimal_c_2nd',
                                   TRUE ~ allocate_type))) %>%
  arrange(id_i, allocate_type) %>%
  select(-rho, -F_star_i, -EH_star_i, -survive) %>% 
  select(id_i, rho_val, everything())

df_alloc_all <- df_alloc_all %>%
  pivot_wider(names_from = allocate_type,
              values_from = checks)

# export
write.csv(df_alloc_all,
  paste0(srt_csv_path, "df_alloc_all_optimal_g47.csv"),
  row.names = TRUE)

```

Export Grouped Average Statistics:

```{r}
ls_svr_groups <- ar_svr_groups
for (svr_group in ls_svr_groups) {

  # group mean
  df_alloc_combine_group_mean <- df_alloc_all %>%
    ungroup() %>% group_by(!!sym(svr_group)) %>%
    summarize(actual_mean = sum(actual*mass)/sum(mass),
              optimal_c_1st_mean = sum(optimal_c_1st*mass)/sum(mass),
              optimal_v_1st_mean = sum(optimal_v_1st*mass)/sum(mass),
              optimal_c_2nd_mean = sum(optimal_c_2nd*mass)/sum(mass),
              optimal_v_2nd_mean = sum(optimal_v_2nd*mass)/sum(mass),
              mass_sum = sum(mass))

  # Export
  write.csv(df_alloc_combine_group_mean,
    paste0(srt_csv_path, "df_alloc_",svr_group, "_optimal_g47.csv"),
    row.names = TRUE)

  # All but Group mean
  ls_svr_groups_oneless <- ls_svr_groups[ls_svr_groups != svr_group]
  df_alloc_combine_group_mean_oneless <- df_alloc_all %>%
    ungroup() %>% group_by(!!!syms(ls_svr_groups_oneless)) %>%
    summarize(actual_mean = sum(actual*mass)/sum(mass),
              optimal_c_1st_mean = sum(optimal_c_1st*mass)/sum(mass),
              optimal_v_1st_mean = sum(optimal_v_1st*mass)/sum(mass),
              optimal_c_2nd_mean = sum(optimal_c_2nd*mass)/sum(mass),
              optimal_v_2nd_mean = sum(optimal_v_2nd*mass)/sum(mass),
              mass_sum = sum(mass))

  # Export
  write.csv(df_alloc_combine_group_mean_oneless,
    paste0(srt_csv_path, "df_alloc_",svr_group,"_without_optimal_g47.csv"),
    row.names = TRUE)

}
```

Average Statistics without Age

```{r}
ls_svr_groups <- ar_svr_groups_noage
for (svr_group in ls_svr_groups) {

  # All but Group mean
  ls_svr_groups_oneless <- ls_svr_groups[ls_svr_groups != svr_group]
  df_alloc_combine_group_mean_oneless <- df_alloc_all %>%
    ungroup() %>% group_by(!!!syms(ls_svr_groups_oneless)) %>%
    summarize(actual_mean = sum(actual*mass)/sum(mass),
              optimal_c_1st_mean = sum(optimal_c_1st*mass)/sum(mass),
              optimal_v_1st_mean = sum(optimal_v_1st*mass)/sum(mass),
              optimal_c_2nd_mean = sum(optimal_c_2nd*mass)/sum(mass),
              optimal_v_2nd_mean = sum(optimal_v_2nd*mass)/sum(mass),
              mass_sum = sum(mass))

  # Export
  write.csv(df_alloc_combine_group_mean_oneless,
    paste0(srt_csv_path, "df_alloc_",svr_group,"_without_noage_optimal_g47.csv"),
    row.names = TRUE)

}

```

### Print and save MASS REV results:

```{r}
# Save REV to table, Stack them
tb_rho_rev_mass_v1_tab <- ls_prc_outputs_zs5_1st$tb_rho_rev_v %>% 
  mutate(objective = 'vlife', 
         constraint = 'optimal_g47',
         allocround = 'first')
tb_rho_rev_mass_c1_tab <- ls_prc_outputs_zs5_1st$tb_rho_rev_c %>% 
  mutate(objective = 'c2020', 
         constraint = 'optimal_g47',
         allocround = 'first')  
tb_rho_rev_mass_v2_tab <- ls_prc_outputs_zs5_2nd$tb_rho_rev_v %>% 
  mutate(objective = 'vlife', 
         constraint = 'optimal_g47',
         allocround = 'second')
tb_rho_rev_mass_c2_tab <- ls_prc_outputs_zs5_2nd$tb_rho_rev_c %>% 
  mutate(objective = 'c2020', 
         constraint = 'optimal_g47',
         allocround = 'second')  
# Stack frames
tb_rho_rev_mass_v_c_tab <- rbind(tb_rho_rev_mass_v1_tab, tb_rho_rev_mass_c1_tab, 
                                 tb_rho_rev_mass_v2_tab, tb_rho_rev_mass_c2_tab)
# export
write.csv(tb_rho_rev_mass_v_c_tab,
  paste0(srt_csv_path, "rev_optimal_g47.csv"),
  row.names = TRUE)
```
